\subsection{Various Payloads}
\label{sec:varioustech}

\subsubsection{Payload size}


\subsubsection{Unicode encoding in JSON}
RFC 4627 \quotes{The application/json Media Type for JavaScript Object Notation} states under section 2.5 \quotes{Strings}:
\begin{quote}
	The representation of strings is similar to conventions used in the C
	family of programming languages.  A string begins and ends with
	quotation marks.  All Unicode characters may be placed within the
	quotation marks except for the characters that must be escaped:
	quotation mark, reverse solidus, and the control characters (U+0000
	through U+001F).

	Any character may be escaped.  If the character is in the Basic
	Multilingual Plane (U+0000 through U+FFFF), then it may be
	represented as a six-character sequence: a reverse solidus, followed
	by the lowercase letter u, followed by four hexadecimal digits that
	encode the character's code point.  The hexadecimal letters A though
	F can be upper or lowercase.  So, for example, a string containing
	only a single reverse solidus character may be represented as
	"\u005C". \cite{rfc4627}
\end{quote}
As escaping any character should be possible in a JSON payload, firewall filters that look for a certain sequence of characters might be evaded by escaping one or more characters from that sequence.


\subsubsection{Unicode normalization}
{\color{red}
\cite{unicode/normalization}
\cite{medium/allypetitt}
}


\subsubsection{Case alternation}
In order to evade regex filerting by the WAF, the case of a payload can be alternated. \cite{medium/allypetitt}
Modern regex flavors allow the application of modifiers to parts of the regular expression.
One such modifier is \verb|(?i)|. It makes the regex case insensitive. \cite{regex/jan} Only when this modifier is not used, can a payload evade regex filtering using case alternation.

Taking the XSS payload \verb|<script>alert('XSS')</script>| as an example, after applying case alternation, it might result in a payload in the form of: \verb|<sCrIpT>alert('XSS')</sCriPt>|.
Another example is file access on a wrongfully public file.
The Windows file system trests file and directory names as case-insensitive by default. \cite{windows/casesensitive}
On a web server hosted on Windows that exposes a .env file with stored secrets, both urls: \\ \verb|http://127.0.0.1:8000/.env| and \verb|http://127.0.0.1:8000/.enV| \\
are treated equally. {\color{red}TODO: verified by the author using the python webserver module on windows 10 [should this be here?]}


\subsubsection{Comment interference}
In some context, comments can be used to break up statements. Regarding SQL, the Oracle Database SQL Reference states:
\begin{quote}
	A comment can appear between any keywords, parameters, or punctuation marks in a statement. You can include a comment in a statement in two ways:
	\begin{itemize}
		\item Begin the comment with a slash and an asterisk (/*). Proceed with the text of the comment. This text can span multiple lines. End the comment with an asterisk and a slash (*/). The opening and terminating characters need not be separated from the text by a space or a line break.
		\item Begin the comment with -- (two hyphens). Proceed with the text of the comment. This text cannot extend to a new line. End the comment with a line break.
	\end{itemize}
	\cite{oracle/sqlcomments}
\end{quote}
Ally Petitt suggests using comments inside SQL statements to break up SQL keywords: \verb|?id=1+un/**/ion+sel/**/ect+1,2,3--| \cite{medium/allypetitt}


\subsubsection{Percent encoding}


\subsubsection{Charset alternation}
To indicate the original media type prior to any applied content encoding, the HTTP \verb|Content-Type| representation header is used.
It can be used in requests by the client to tell the server what type of data is actually sent.
\verb|charset| is a possible directive, that specifies the character encoding standard.
It can be supplied with the \verb|Content-Type| header. \cite{http/contenttype}
If a web server is supporting requests in different encoding standards, but the WAF is not configured to parse certain encoding standards, the WAF may not recognize such encoded request as malicious.

The payload \verb|'<script>alert("xss")</script>'| becomes \\
\verb|'L%A2%83%99%89%97%A3n%81%93%85%99%A3M%7F%A7%A2%A2%7F%5DLa%A2%83%99%89%97%A3n'|
after encoding the payload to the charset \verb|IBM037| followed by percent encoding. \\
This differs from the same payload in \verb|UTF-8| followed by percent encoding: \\
\verb|'%3Cscript%3Ealert%28%22xss%22%29%3C%2Fscript%3E'| \\
\verb|UTF-8| encoding is the standard for URIs according to RFC-3986. \cite{rfc3986} \\
Technique by \cite{medium/allypetitt}.
